paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

The original analysis and our replication of this analysis are limited by the use of data from only 18 states.  We addressed this shortcoming in our extension, though our extension still does not have data for all states and/or all counties. Further, our replication of the original analysis as well as our extensions and expansions of said analysis are limited by the fact that state-level legislative data is only available for the years 2000, 2010, and 2020. More detailed legislative information is available for more recent years (roughly 2018 to the present), but abortion count data for these years is not yet released. Further analyses with more recent, detailed legislative data and abortion counts from more recent years would greatly add to the present analyses and could also allow for a longitudinal approach. The original analysis and our own are limited by the calculating abortion rates using total number of women, rather than number of women of reproductive age.

>>>>

The main limitations of these analyses are due to missing data. Both the original analysis and our replication of this analysis are limited by the use of data from only 18 states.  We addressed this shortcoming in our extension, though our extension still does not have data for all states and/or all counties. Further, our replication of the original analysis as well as our extensions and expansions of said analysis are limited by the fact that state-level legislative data is only available for the years 2000, 2010, and 2020. More detailed legislative information is available for more recent years (roughly 2018 to the present), but abortion count data for these years is not yet released. Further analyses with more recent, detailed legislative data and abortion counts from more recent years would greatly add to the present analyses and could also allow for a more longitudinal approach. The original analysis and our own are also limited by the fact that abortion rates are calculated using total number of women, rather than number of women of reproductive age - this is due to the lack of data on population statistics stratified by age. Further, the data used in our extension is only by state, rather than by county, as previously discussed, due to suppression of data for the purpose of preserving anonymity.
